\documentclass[12pt,letterpaper]{article}

\def\myauthor{Matteo Rizzuto}
\def\mytitle{mr-vita}
\def\myemail{mrizzuto@mun.ca}
\def\myweb{matteorizzuto}
\def\mytwitter{@MatteoRiz}
\def\myorcid{0000-0003-3065-9140}
\def\myphone{+39 (320) 196 2339}
\def\mykeywords{
  matteo rizzuto,
  resume,
  curriculum,
  vita,
  curriculum vita,
  cv,
  matteo,
  rizzuto,
  mr
}

\setlength\parindent{0pt}

\newenvironment{itemize*}%
{\begin{itemize}%
  \setlength{\itemsep}{2.5pt}}%
{\end{itemize}}

\usepackage{url}
\usepackage{fancyhdr}
\usepackage{lastpage}
%\usepackage{ocgtools}
\usepackage{enumitem}
\setlist{nolistsep,leftmargin=0.15in}
\usepackage[log-declarations=false]{xparse}
\usepackage[garamond]{mathdesign}
\usepackage[no-math]{fontspec}
% \usepackage{fontawesome}
\usepackage{fontawesome5}
\usepackage{microtype}
\usepackage[margin=1.125in,top=1.3in,right=1in,left=2in]{geometry}
\usepackage[strict]{changepage}
\usepackage{ocgx2}
%\usepackage[T1]{fontenc}
\usepackage[
  ocgcolorlinks,
  urlcolor={[rgb]{0,0,0.4}},
  unicode,
  plainpages=false,
  pdfpagelabels,
  pdftitle={\mytitle},
  pdfauthor={\myauthor},
  pdfkeywords={\mykeywords}
]{hyperref}

% fix ocgcolor link breaking; thanks due to Benjamin Lerner
% (http://goo.gl/VZKR7M)
\setmainfont{Adobe Garamond Pro}
\makeatletter
\AtBeginDocument{%
  \newlength{\temp@x}%
  \newlength{\temp@y}%
  \newlength{\temp@w}%
  \newlength{\temp@h}%
  \def\my@coords#1#2#3#4{%
    \setlength{\temp@x}{#1}%
    \setlength{\temp@y}{#2}%
    \setlength{\temp@w}{#3}%
    \setlength{\temp@h}{#4}%
    \adjustlengths{}%
    \my@pdfliteral{\strip@pt\temp@x\space\strip@pt\temp@y\space\strip@pt\temp@w\space\strip@pt\temp@h\space re}}%
  \ifpdf
    \typeout{In PDF mode}%
    \def\my@pdfliteral#1{\pdfliteral page{#1}}% I don't know why % this command...
    \def\adjustlengths{}%
  \fi
  \ifxetex
    \def\my@pdfliteral #1{\special{pdf: literal direct #1}}% isn't equivalent to this one
    \def\adjustlengths{\setlength{\temp@h}{-\temp@h}\addtolength{\temp@y}{1in}\addtolength{\temp@x}{-1in}}%
  \fi%
  \def\Hy@colorlink#1{%
    \begingroup
      \ifHy@ocgcolorlinks
        \def\Hy@ocgcolor{#1}%
        \my@pdfliteral{q}%
        \my@pdfliteral{7 Tr}% Set text mode to clipping-only
      \else
        \HyColor@UseColor#1%
      \fi
  }%
  \def\Hy@endcolorlink{%
    \ifHy@ocgcolorlinks%
      \my@pdfliteral{/OC/OCPrint BDC}%
      \my@coords{0pt}{0pt}{\pdfpagewidth}{\pdfpageheight}%
      \my@pdfliteral{F}% Fill clipping path (the url's text) with current color
      \my@pdfliteral{EMC/OC/OCView BDC}%
      \begingroup%
        \expandafter\HyColor@UseColor\Hy@ocgcolor%
        \my@coords{0pt}{0pt}{\pdfpagewidth}{\pdfpageheight}%
        \my@pdfliteral{F}% Fill clipping path (the url's text) with \Hy@ocgcolor
      \endgroup%
      \my@pdfliteral{EMC}%
      \my@pdfliteral{0 Tr}% Reset text to normal mode
      \my@pdfliteral{Q}%
    \fi
    \endgroup
  }%
}
\makeatother
% end fixes

% \newcommand{\ML}{\textsc{Matlab}}
% \newcommand{\Simu}{Simulink}
% \newcommand{\MLS}{\ML{}/\Simu{}}
% \newcommand{\apdl}{\textsc{APDL}}
% \newcommand{\ansys}{\textsc{Ansys}}
% \newcommand{\fluent}{\textsc{Fluent}}
% \newcommand\CPP{C/C\ensuremath{+}\ensuremath{+}}
% \newcommand{\Star}{\textsc{Star-CCM\ensuremath{+}}}

\newcommand{\mhead}[1]{\leavevmode\marginpar{\sffamily\footnotesize #1}}
\newcommand{\rdate}[1]{{\addfontfeature{Numbers=OldStyle} \hfill #1}}
\renewcommand{\date}[1]{{\addfontfeature{Numbers=OldStyle} #1}}
\renewcommand{\labelitemi}{-}

\setmainfont[
  Ligatures={TeX,Common},
  BoldFont={AGaramondPro-Semibold},
]{Adobe Garamond Pro}
\setsansfont[
  Ligatures={TeX,Common},
  Letters=SmallCaps,
  Color=005100,
]{Adobe Garamond Pro}

\setmonofont[Scale=0.85]{FontAwesome}

\makeatletter % fix for \hrulefill w/ mathdesign package
\def\hrulefill{\leavevmode\leaders\hrule\hfill\kern\z@}
\makeatletter

\begin{document} \flushbottom
\pagestyle{fancy} \setlength\headwidth{6.5in}
\lhead{\textsc{matteo~rizzuto}}
\rhead{\textsc{\thepage{}~of~\pageref*{LastPage}}} \cfoot{}
\thispagestyle{empty}
\begin{adjustwidth}{-1in}{}
{\Huge
  {\textsc{%
    {\addfontfeature{Style=TitlingCaps}M}atteo~
    {\addfontfeature{Style=TitlingCaps}R}izzuto}
  }
}
\hfill\hfill\hfill
{
  \begin{minipage}[b]{2in}
    \flushleft \footnotesize
    Ecosystem Ecology Lab\\
    Department of Biology \\
    Memorial University of Newfoundland and Labrador\\
    St.\ John's,\ NL, Canada
  \end{minipage}
  \hfill
  \begin{minipage}[b]{1.5in}
    \flushright \footnotesize
    \href{tel:\myphone}{\myphone} \\ %\texttt{}~
    \href{mailto:\myemail}{\myemail} \\
    \href{https://www.linkedin.com/in/\myweb}{\texttt{\faLinkedin}}~\href{https://\myweb.github.io}{\texttt{\faGithub}~\myweb}\\
    \href{https://twitter.com/\mytwitter}{\texttt{\faTwitter}~\mytwitter}\\
    \href{https://orcid.org/0000-0003-3065-9140}{\texttt{\faOrcid}~\myorcid}
  \end{minipage}
}\par
\hrulefill
\end{adjustwidth}
\reversemarginpar
\setlength\marginparwidth{0.85in}

\smallskip
% \section{Education}

\mhead{Education}%
\textbf{Ph.D. Candidate}, \emph{\href{http://www.mun.ca/biology}{Biology}} \rdate{2016--\textsc{present}}\\
Memorial University of Newfoundland and Labrador, St.\ John's, NL, Canada
\begin{itemize*}
  \item Thesis: Bottom-up or top-down? Intraspecific variability, resource quality, and space use in the Boreal Forest
  \item Supervisor: Dr.~Shawn J.~Leroux
\end{itemize*}

\medskip
\textbf{Master of Research (Distinction)},
\emph{\href{https://www.imperial.ac.uk/study/pg/life-sciences/ecology-evolution-conservation-research/}{Ecology, Evolution, and Conservation}} \rdate{2013--2014}\\
Imperial College London-Silwood Park, Ascot, UK
\begin{itemize*}
  \item Research Projects:
  \begin{itemize*}
    \item The scaling of activity budgets in carnivores; Supervisors: Dr.~Samraat Pawar and Dr.~Chris Carbone
    \item Comparison of two commonly used methods to estimate species diversity: dung counts and camera trapping; Supervisors: Prof.~Mick Crawley and Prof.~Joris Cromsigt
  \end{itemize*}
\end{itemize*}

\medskip
\textbf{Master of Science}, \emph{\href{https://goo.gl/rCzbq7}{Evolution of Animal and Human Behaviour}} \rdate{2009--2012}\\
University of Turin, Turin, Italy
\begin{itemize*}
  \item Thesis: Predator-prey interactions: feeding ecology of the Wolf (\textit{Canis lupus}) and anti-predator behaviour of the Chamois (\textit{Rupicapra rupicapra}) in the Western Alps
  \item Supervisor: Dr.~Francesca Marucco
\end{itemize*}

\medskip
\textbf{Bachelor of Science (Honours)},
\emph{\href{http://biologia.campusnet.unito.it/do/home.pl}{Biology}} \rdate{2004--2009}\\
University of Turin, Turin, Italy
\begin{itemize*}
  \item Thesis: Individual characteristics of vocalisations emitted during the song of \textit{Indri indri}
  \item Supervisors: Prof.~Cristina Giacoma and Dr.~Marco Gamba
\end{itemize*}

\bigskip
% \section{Publications}
\mhead{Publications}%
\begingroup
\small
Note: for papers where I am first author, I led study design, data collection, analysis, and writing. For papers where I am fourth author or later, I contributed to ideas, data collection, and writing.
\endgroup

\smallskip
\emph{Peer Reviewed} (* stands for equal contribution)
\begin{itemize*}
  \item Ellis-Soto, D.\textsuperscript{*}, Ferraro, K. M.\textsuperscript{*}, \textbf{Rizzuto, M.}, Briggs, E., Monk, J. D., and Schmitz, O. J. A methodological roadmap to quantify animal-vectored spatial ecosystem subsidies.~Accepted.~\emph{Journal of Animal Ecology},~Available at:~\href{https://doi.org/10.1111/1365-2656.13538}{10.1111/1365-2656.13538}
  \item Richmond, I. C., Leroux, S. H., Vander Wal, E., Heckford, T. R., \textbf{Rizzuto, M.}, Balluffi-Fry, J., Kennah, J., Wiersma, Y. F.~(\date{2020}) Temporal variation and its drivers in the elemental traits of four boreal plant species.~\emph{Journal of Plant Ecology} \textbf{14} (3), 398--413.~Available at:~\href{https://doi.org/10.1093/jpe/rtaa103}{10.1093/jpe/rtaa103}.
  \item Balluffi-Fry, J., Leroux, S. J., Wiersma, Y. F., Heckford, T. R., \textbf{Rizzuto, M.}, Richmond, I. C., Vander Wal, E.~(\date{2020}) Quantity-quality trade-offs revealed using a multiscale test of herbivore resource selection on elemental landscapes.~\emph{Ecology and Evolution} \textbf{10} (24), 13847--13859.~Available at:~\href{https://doi.org/10.1002/ece3.6975}{10.1002/ece3.6975}
  \item \textbf{Rizzuto, M.}, Leroux, S. J., Vander Wal, E., Wiersma, Y. F., Heckford, T. R., Balluffi-Fry, J.~(\date{2019}) Patterns and potential drivers of intraspecific variability in the body C, N, and P composition of a terrestrial vertebrate, the snowshoe hare (\textit{Lepus americanus}).~\textit{Ecology and Evolution} \textbf{9} (24), 14453--14464.~Available at:~\href{https://doi.org/10.1002/ece3.5880}{10.1002/ece3.5880}
  \item \textbf{Rizzuto, M.}, Carbone, C., and Pawar, S.~(\date{2018}) Foraging constraints reverse the scaling of activity time in carnivores.~\emph{Nature Ecology and Evolution} \textbf{2} (2), 247--253. Available at: \href{https://doi.org/10.1038/s41559-017-0386-1}{10.1038/s41559-017-0386-1} \rdate{\textbf{\textit{Cover story}}}
\end{itemize*}

% \bigskip
% \bigskip
% \newpage
\emph{In Progress}
\begin{itemize*}
  \item \textbf{Rizzuto, M.}, Leroux, S.J., Vander Wal, E., Richmond, I. C., Heckford, T. R., Balluffi-Fry, J., Wiersma, Y. F. Forage stoichiometry predicts the home range size of a small terrestrial herbivore. In review.~\emph{Oecologia}, manuscript id: OECO-D-21-00094.\\ Preprint: \href{https://doi.org/10.1101/2020.08.13.248831}{10.1101/2020.08.13.248831}
  \item Balluffi-Fry, J., Leroux, S.J., Wiersma, Y.F., Richmond, I.C., Heckford, T.R., \textbf{Rizzuto, M.}, Kennah, J.L., Vander Wal, E. Integrating plant stoichiometry and feeding experiments: state-dependent forage choice and its implications on body mass. In review. \emph{Oecologia}, manuscript id: OECO-D-21-00125.\\ Preprint: \href{https://doi.org/10.1101/2021.02.16.431523}{10.1101/2021.02.16.431523}
  \item Heckford, T. R., Leroux, S. J., Vander Wal, E., \textbf{Rizzuto, M.}, Balluffi-Fry, J., Richmond, I. C., Wiersma, Y. F. Foliar elemental niche responses of balsam fir (\textit{Abies balsamea}) and white birch (\textit{Betula papyrifera}) to differing community types across geographic scales. In revision, \emph{Functional Ecology}, manuscript id: FE-2020-00432.
  \item Heckford, T. R., Leroux, S. J., Vander Wal, E., \textbf{Rizzuto, M.}, Balluffi-Fry, J., Richmond, I. C., Wiersma, Y. F. Does where you live influence what you’re made of?Spatial correlates of chemical traits across commonly occurring boreal plants. In review.~\emph{Landscape Ecology}, manuscript id: LAND-D-21-00046.\\ Preprint: \href{https://doi.org/10.1101/2021.01.26.428320}{10.1101/2021.01.26.428320}
  \item Little, C. J.\textsuperscript{*}, \textbf{Rizzuto, M.}\textsuperscript{*}, Luhring, T. M., Monk, J. D., Nowicki, R. J., Paseka, R. E., Stegen, J. C., Symons, C. C., Taub, F. B., Yan, J. D. L. Filling the Information Gap in Meta-Ecosystem Ecology. Preprint: \href{https://doi.org/10.32942/osf.io/hc83u}{10.32942/osf.io/hc83u}
  \item Richmond, I. C., Balluffi-Fry, J., Vander Wal, E., Leroux, S. J., \textbf{Rizzuto, M.}, Heckford, T. R., Kennah, J. L., Riefesel, G. R., Wiersma, Y. F. Individual snowshoe hares manage risk differently: Integrating stoichiometric distribution models and foraging ecology. In review.~\emph{Journal of Mammalogy}, manuscript id: JMAMM-2021-026.
\end{itemize*}

\medskip
\emph{Scientific Outreach}
\begin{itemize*}
\item Cagnacci, F., Rocca, M., Nicoloso, S., Ossi, F., Peters, W., Mancinelli, S., Valent, M., \textbf{Rizzuto, M.}, Hebblewhite, M.~(\date{2013}).~\emph{Il progetto 2C2T.}~Il Cacciatore Trentino, 93, 4--15.
\end{itemize*}

\bigskip
% \section{Conference Presentations}
\mhead{Conference\\ Presentations}%
\emph{Talks}
\begin{itemize*}
\setlength\itemsep{0.25em}
\item \textbf{Rizzuto, M.}, Leroux, S. J., Vander Wal, E., Wiersma, Y., Heckford, T. R., Balluffi-Fry, J. \emph{Ontogeny and Ecological Stoichiometry of Snowshoe hares (Lepus americanus) in the Boreal Forests of Newfoundland.} Canadian Society for Ecology and Evolution Annual General Meeting, Guelph, ON, Canada. \date{18--21 \textsc{jul.}~2018}
\item \textbf{Rizzuto, M.}, Carbone, C., and Pawar, S. \emph{Bio-mechanical constraints on foraging reverse the scaling of activity rate among carnivores.} Canadian Society for Ecology and Evolution Annual General Meeting, St.\ John's, NL, Canada. \date{7--11 \textsc{jul.}~2016}
\end{itemize*}

% \medskip
% \emph{Co-authored}
% \vspace{0.25em}
% \begin{itemize*}
% \setlength\itemsep{0.25em}
% \item Heckford, T. R.\(^*\), Leroux, S. J., Vander Wal, E., \textbf{Rizzuto, M.}, Balluffi-Fry, J., Richmond, I., Wiersma, Y. \textit{Investigating the effect of competition on the intraspecific variability of foliar elemental traits.} Atlantic Society of Fish and Wildlife Biologists Annual General Meeting, Corner Brook, NL, Canada. \date{21--23 \textsc{oct.}~2018}
% \item Heckford, T. R.\(^*\), Leroux, S. J., Vander Wal, E., \textbf{Rizzuto, M.}, Balluffi-Fry, J., Wiersma, Y. \textit{Spatial Variability in the Elemental Composition of Plants: Implications for Herbivores on the Resource Stoichiometric Landscape.} Canadian Society of Zoologists Annual General Meeting, St.\ John’s, NL, Canada. \date{7--11 \textsc{may}~2018}
% \item Heckford, T. R.\(^*\), Leroux, S. J., Vander Wal, E., \textbf{Rizzuto, M.}, Balluffi-Fry, J., Wiersma, Y. \textit{From Elements to Communities to Ecosystems.} Nature Newfoundland and Labrador, St.\ John’s, NL, Canada. \date{15 \textsc{feb.}~2018}
% \item Heckford, T. R.\(^*\), Leroux, S. J., Vander Wal, E., \textbf{Rizzuto, M.}, Balluffi-Fry, J., Wiersma, Y. \textit{The stoichiometric landscape: mapping the biogeochemical matrix with wildlife in mind.} Geomatics Atlantic Conference, St.\ John’s, NL, Canada. \date{23--24 \textsc{nov.}~2017}
% \end{itemize*}

\medskip
\emph{Posters}%
\begin{itemize*}
\setlength\itemsep{0.25em}
\item \textbf{Rizzuto, M.}, Leroux, S. J., Vander Wal, E., Wiersma,
Y., Heckford, T. R., Balluffi-Fry, J. \emph{Beyond Diffusion: Animal-Mediated Nutrient Transport at Different Spatial Scales.} ``Unifying Ecology Across Scales'' Gordon Research Seminar and Conference, Biddeford, ME, USA.\ \date{21--27 \textsc{jul.}~2018}
\end{itemize*}

% \medskip
% \emph{Co-authored}
% \vspace{0.25em}
% \begin{itemize*}
% \setlength\itemsep{0.25em}
% \item Balluffi-Fry J.\(^*\), Vander Wal E., Leroux S. J., Wiersma Y., Heckford T. R., \textbf{Rizzuto M.} \emph{Using forage elemental
% composition to test for scale-dependent quality and quantity trade-offs in moose.} Canadian Society for Ecology and Evolution Annual General Meeting, Guelph, ON, Canada. \date{18--21 \textsc{jul.}~2018}
% \item Balluffi-Fry J.\(^*\), Vander Wal E., Leroux S. J., Wiersma Y., Heckford T. R., \textbf{Rizzuto M.} \emph{Multi-scale test of moose foraging
% strategy using quantitative elemental measures for forage quality and
% quantity.} Memorial University Biology Graduate Student Symposium, St.\ John's,
% NL, Canada. \date{11--13 \textsc{apr.}~2018}
% \item Heckford, T. R.\(^*\), Leroux, S. J., Vander Wal, E., \textbf{Rizzuto, M.}, Balluffi-Fry, J., Wiersma, Y. \emph{Constructing the
% Stoichiometric Landscape: Spatial Correlates of Plant Elemental Composition.}
% Memorial University Biology Graduate Student Symposium, St.\ John's, NL, Canada. \date{11--13 \textsc{apr.}~2018}
% \item Heckford, T. R.\(^*\), Leroux, S. J., Vander Wal, E., \textbf{Rizzuto,
% M.}, Wiersma, Y. \emph{A tale of two trees: stoichiometry of balsam fir and
% white birch in the boreal forest.} Canadian Society for Ecology and Evolution
% Annual General Meeting, Victoria, BC, Canada. \date{7--11 \textsc{may}~2017}
% \end{itemize*}

\bigskip
% \section{Honors and Awards}
\mhead{Honors \& \newline Awards}%
\par\vspace{-\baselineskip}\begin{itemize*}
\item Mitacs Research Training Award, Mitacs Canada \rdate{2020}
\item First Place, H5P Maker Session, Centre for Innovation in Teaching and Learning, Memorial University of Newfoundland and Labrador \rdate{2019}
    % \begin{itemize*}
    %     \item[] \textit{Awarded to the best HTML5 interactive learning object created during the session}
    % \end{itemize*}
\item Mitacs Globalink Research Award, Mitacs Canada \rdate{2018}
    % \begin{itemize*}
    %     \item[] \textit{Awarded to senior graduate students to conduct research  abroad}
    % \end{itemize*}
\item Dean's Doctoral Award, \rdate{2016--2018}\\ Memorial University of Newfoundland and Labrador 
    % \begin{itemize*}
    %     \item[] \textit{Awarded to Ph.D. students based on academic excellence and research potential}
    % \end{itemize*}
\item Graduated with Distinction, Imperial College London \rdate{2014}
    % \begin{itemize*}
    %     \item[] \textit{Awarded to the top 5\% of all Master's students in the \date{2013-2014} cohort}
    % \end{itemize*}
\item Erasmus-LLP Scholarship, University of Turin \rdate{2010}
    % \begin{itemize*}
    %     \item[] \textit{Awarded to participants in the European Union's Erasmus student exchange program}
    % \end{itemize*}
\end{itemize*}

\bigskip
% \section{Research Experience}
\mhead{Research \newline Experience}%
\textbf{Visiting Assistant in Research}, \emph{Schmitz Lab} \rdate{\textsc{feb.}-\textsc{apr.}~2019}\\
School of the Environment, Yale University, New Haven, CT
\begin{itemize*}
  \item Collaboration to develop a mathematical metaecosystem model describing animal-mediated nutrient transport across ecosystem boundaries
  \item Reviewed metaecosystem, metapopulation, and animal movement literature
  \item Performed simulations of ecosystem persistence over time under different animal movement and nutrient transport scenarios
\end{itemize*}

\medskip
\textbf{Research Assistant}, \emph{Pawar Lab} \rdate{\textsc{jan.}-\textsc{mar.}~2016}\\
Imperial College London-Silwood Park, Ascot, UK
\begin{itemize*}
  \item Digitized data from terrestrial plant thermal response from published studies
  \item Assisted with database management and cleanup, and formation of new team members
  % \item Part of a larger project aimed at analyzing the effects of temperature on the physiology of different plant phyla
\end{itemize*}

\medskip
\textbf{Research Assistant}, \emph{Tsaobis Baboon Project} \rdate{\textsc{jun.}-\textsc{oct.}~2015}\\
 Zoological Society of London, London, UK
\begin{itemize*}
  % \item Three months placement, part of a long-term research project on the ecology of Chacma baboons (\textit{P. ursinus}), in Tsaobis Leopard Nature Park (Namibia)
  \item Assisted with collection of behavioural and population data from two troops of wild, habituated Chacma baboons, and with plant phenology surveys
  % in the Tsaobis riverbed and nearby hills
  % \item Improved my knowledge of behavioural sampling techniques, primate and desert ecology, as well as of project management and of GPS equipment
\end{itemize*}

\medskip
\textbf{Research Assistant}, \emph{Roe \& Red deer in Trentino \& Technology Project} \rdate{\textsc{jun.}-\textsc{sept.}~2013}\\ Trento, Italy
\begin{itemize*}
  \item Studied the migratory behaviour of roe deer using radio-tracking techniques (GPS, VHF), plant phenology surveys, and pellet decay rate analyses
  \item Intensive fieldwork in a physically demanding environment, under harsh weather conditions
  % \item Worked with researchers from the Ungulate Ecology Lab of the University of Montana, as part of an international team coalescing a variety of different backgrounds and expertise
  % \item Greatly enhanced my radio-tracking, plant and pellet identification and organizational skills
\end{itemize*}

\medskip
\textbf{Graduate Intern}, \emph{Piedmont Wolf Project} \rdate{\textsc{jun.}-\textsc{dec.}~2011}\\
Maritime Alps Nature Park, Entraque (CN), Italy
\begin{itemize*}
  \item Designed and performed a study of the predator-prey interactions of wolves and chamois in the Maritime Alps Natural Park
  \item Managed all aspects of the project, from behavioural sampling to prey identification by hair analysis to scat specimen preparation for DNA analyses
  % \item Vastly enhanced my fieldwork, laboratory and time-management skills
\end{itemize*}

\medskip
\textbf{Undergraduate Intern}, \emph{Ethology Lab} \rdate{\textsc{jun.}~2008-\textsc{mar.}~2009}\\
University of Turin, Turin, Italy
\begin{itemize*}
  \item Bioacoustics study of the Indri lemur, testing for potential identification of lemurs from individuals' contributions to the family group song
\end{itemize*}

% \bigskip
% \section{Teaching Experience}
\mhead{Teaching \newline Experience}%
\textbf{Guest Lecturer}, \emph{Department of Biology}\\
Memorial University of Newfoundland and Labrador, St.\ John's, NL, Canada\\
\textit{Models in Biology} \rdate{\textsc{winter} 2020} % external
\begin{itemize*}
    \item Lecture: Classical Models in Ecology
    \item Lecture: Models of Species Interactions
    \item Lecture: Meta-ecology Models
\end{itemize*}
\vspace{0.25em}

\textbf{Teaching Assistant}, \emph{Department of Biology}\\
Memorial University of Newfoundland and Labrador, St.\ John's, NL, Canada\\
% BIOL~2600: Principles of Ecology \rdate{\textsc{fall} 2018} % internal
\textit{Principles of Ecology} \rdate{\textsc{fall} 2018} % external
\begin{itemize*}
    % \item Organized and run supporting activities for the course
    \item Managed the online learning section of the course, developing weekly new content introducing students to preeminent ecologists
    \item Provided administrative and academic support to students
    % \item Marked midterms and final exams
\end{itemize*}
\vspace{0.25em}
% BIOL~1002: Principles of Biology \rdate{\textsc{winter} 2017} % internal
\textit{Principles of Biology} \rdate{\textsc{winter} 2017} % external
\begin{itemize*}
    % \item Demonstrator during practical laboratories
    \item Supported students during practical laboratories
    % and in preparing exams
    \item Invigilated midterm and final exams, marked weekly lab reports
\end{itemize*}

\smallskip
\textbf{Undergraduate Teaching Assistant}, \emph{Department of Life Sciences}\\
Imperial College London, London, UK \\
\textit{Ecology} \rdate{\textsc{spring} 2015} % , 2\(^{nd}\) year course
\begin{itemize*}
    % \item Demonstrator for the course's field trip to Silwood Park Campus
    \item Helped students collect data and plan analyses for final projects
\end{itemize*}
\vspace{0.25em}
\textit{Behavioral Ecology} \rdate{\textsc{winter} 2015} % , 2\(^{nd}\) year course
\begin{itemize*}
    % \item Demonstrator for the course's practical laboratories
    \item Assisted in laboratory setup for weekly practicals
    \item Helped student design analyses on data collected during practicals
\end{itemize*}
\vspace{0.25em}
\textit{Introduction to Biological Statistics} \rdate{\textsc{fall} 2014} % , 2\(^{nd}\) year course
\begin{itemize*}
    % \item Demonstrator during the course's lectures
    \item Helped students learn base and advanced R language
    % \item Facilitated Q\&A sessions ahead of final exams
\end{itemize*}

\smallskip
\textbf{Graduate Teaching Assistant}, \emph{Department of Life Sciences}\\
Imperial College London-Silwood Park, Ascot, UK \\
\textit{Statistics} \rdate{\textsc{fall} 2014}
\begin{itemize*}
  % \item Demonstrator during laboratory practicals
  \item Assisted students with R coding and in developing statistical analyses
\end{itemize*}
% \vspace{0.25em}
% \newpage
\textit{Macroecology and Climate Change} \rdate{\textsc{fall} 2014}
\begin{itemize*}
  % \item Demostrator for practical lectures
  \item Assisted students using the species distribution software Maxent
\end{itemize*}

\bigskip
% \section{Service}
\mhead{Service}
Manuscript reviewer for \emph{Ecology and Evolution} and \emph{Science of the Total Environment}.

\bigskip
% \section{Professional Development}
\mhead{Professional\\ Development}
% \par\vspace{-\baselineskip}
\emph{Courses}
\begin{itemize*}
    \item \textbf{Becoming a More Equitable Educator: Mindsets and Practices}, \rdate{\textsc{mar.-jun.}~2020}\\
    \emph{MIT Teaching Systems Lab}\\
    Delivered online through \href{www.edx.org}{edX.org}
    \item \textbf{Teaching Skills Enhancement Program}, \rdate{\textsc{sept.-aug.}~2020}\\
    \emph{Centre for Innovation in Teaching and Learning}\\ Memorial University of Newfoundland and Labrador, St.\ John's, NL, Canada
\end{itemize*}
% \medskip
% \newpage
\emph{Workshops}
\begin{itemize*}
    \item \textbf{Reproducible Research through Open Science}, \rdate{11~\textsc{june}~2020}\\
    \emph{Canadian Institute for Ecology and Evolution \& NSERC-CREATE ``Living Data Project''}\\
    Attended online through \href{https://osf.io/p7r5d/}{osf.io}
    \item \textbf{Teaching Inclusively \& Equitably Online}, \rdate{21~\textsc{may}~2020}\\
    \emph{American Society for Engineering Education \& NSF INCLUDES Aspire Alliance}\\
    Attended online through Blackboard Collaborate Ultra
    \item \textbf{H5P Maker Session}, \rdate{24~\textsc{oct.}~2019}\\
    \emph{Centre for Innovation in Teaching and Learning}\\ Memorial University of Newfoundland and Labrador, St.\ John's, NL, Canada
    \item \textbf{Community of Inquiry Coffee Break: Open Access}, \rdate{23~\textsc{oct.}~2019}\\
    \emph{Centre for Innovation in Teaching and Learning}\\ Memorial University of Newfoundland and Labrador, St.\ John's, NL, Canada
    \item \textbf{Open Access and Scholarly Publishing}, \rdate{22~\textsc{oct.}~2019}\\
    \emph{Centre for Innovation in Teaching and Learning}\\ Memorial University of Newfoundland and Labrador, St.\ John's, NL, Canada
    \item \textbf{Four Things to Consider for Graduate Student Teaching}, \rdate{8~\textsc{nov.}~2018}\\
    \emph{Enhanced Development of the Graduate Experience}\\ Memorial University of Newfoundland and Labrador, St.\ John's, NL, Canada
    \item \textbf{AARMS CRG Software Carpentry Workshop}, \rdate{27~\textsc{may}~2017}\\
    \emph{The Carpentries}\\
    Memorial University of Newfoundland and Labrador, St.\ John's, NL, Canada
\end{itemize*}

\bigskip
% \section{Volunteer Experience}
\mhead{Volunteer\\ Experience}%
\textbf{Communications Officer}, \emph{Biology Graduate Student Association} \rdate{2019--2020}\\
Memorial University of Newfoundland and Labrador, St.\ John's, NL, Canada
\begin{itemize*}
  \item Managed the Association's weekly newsletter, website, and all of its social media presence
  % \item Coordinated on- and off-campus advertisement efforts for the Association's activities
\end{itemize*}

\smallskip
\textbf{Chair}, \emph{Biology Graduate Student Association} \rdate{2018--2019}\\
Memorial University of Newfoundland and Labrador, St.\ John's, NL, Canada
\begin{itemize*}
  % \item Collaborated with the Head of the Department of Biology's Office to involve graduate students in administrative tasks
  \item Designed, funded, and run ``The Balanced Student: stress and work management for graduate students'', a workshop series on graduate students mental health and wellness
  \item Hosted a Student-Supervisor Relationship workshop during the Graduate Core Seminar course for new graduate students
  \item Coordinated the activities of the Executive Committee, focusing on fundraising and community outreach
\end{itemize*}

\smallskip
\textbf{Seminar Coordinator}, \emph{Biology Graduate Student Association} \rdate{2017--2018}\\
Memorial University of Newfoundland and Labrador, St.\ John's, NL, Canada
\begin{itemize*}
  \item Organized and run the weekly Seminar series for the Department of Biology, in a team of three coordinators
  % \item Approached, scheduled and managed potential speakers, from both within and outside the Department and the Province
  \item Helped in organizing the annual Symposium showcasing the research produced by the Department's graduate students
  \item Contributed to the Association's fundraising and outreach activities
\end{itemize*}

\smallskip
\textbf{Youth Educator}, \emph{OASI-Operazione Mato Grosso} \rdate{2000--2013}\\
Turin, Italy
\begin{itemize*}
  \item Volunteer work with children and teenagers in primary, secondary and high school, in Turin, Italy, and at the Hospital S{\~a}o Juli{\~a}o in Campo Grande, MS, Brazil
  % \item Taught me the value of hard work and developed my publication relationship, oratory and teamwork skills
\end{itemize*}

\smallskip
\textbf{Team Leader}, \emph{XX Winter Olympic and IX Paralympic Games} \rdate{2005--2006}\\
Turin, Italy
\begin{itemize*}
  \item Organized and supervised daily activities of a team of 10 volunteers in the Protocol Crew, International Relations and Services
  % \item Provided initial containment of emergencies, customer assistance, and ensured my team’s welfare
  % \item Greatly developed my leadership and problem solving skills
\end{itemize*}

% \bigskip
% \mhead{Professional\\ Experience}%
% \textbf{Assistant Surveyor}, \emph{Catherine Bickmore Associates Ltd.} \rdate{\textsc{may}-\textsc{jun.}~2015}\\
% London, UK
% \begin{itemize*}
%   \item Involved in reptile and amphibian censuses in Kent, Wiltshire and Cambridgeshire
%   % \item Expanded my knowledge of amphibian and reptile ecology, of ecological survey techniques and of the mechanisms of environmental consultancy
% \end{itemize*}
\bigskip
% \section{Professional Affiliations}
\mhead{Professional\\ Affiliations}%
\par\vspace{-\baselineskip}\begin{itemize}
  \item[] Canadian Society of Ecology and Evolution \rdate{2016--2021}
\end{itemize}

\bigskip
% \section{Conferences Attended}
\mhead{Conferences\\ Attended}
\par\vspace{-\baselineskip}\begin{itemize*}
  \item \emph{``Unifying Ecology Across Scales''} \rdate{21--27 \textsc{jul.} 2018}\\
  \emph{Gordon Research Seminar and Conference}\\ Biddeford, ME, USA
  \item \emph{Canadian Society for Ecology and Evolution Annual General Meeting} \rdate{18--21 \textsc{jul.} 2018}\\Guelph, ON, Canada
  \item \emph{Canadian Society for Ecology and Evolution Annual General Meeting} \rdate{7--11 \textsc{jul.} 2016} \\St.\ John's, NL, Canada
  \item \emph{From Energetics to Macro Ecology:} \rdate{14--15 \textsc{nov.} 2013}\\ \textit{Carnivore Responses to Environmental Change}\\Zoological Society of London, London, UK
  \item \emph{Euroscience Open Forum} \rdate{2--7 \textsc{jul.} 2010}\\Turin, Italy
  \item \emph{XIX Congress of the Italian Primatological Society} \rdate{1--3 \textsc{apr.} 2009}\\ Asti, Italy
\end{itemize*}

\bigskip
% \section{Software Proficiency}
\mhead{Software\\ Proficiency}%
% \emph{Working knowledge}\newline%—comfortable using in a professional setting
R,
RStudio,
Mathematica,
\LaTeX{},
Markdown,
Git,
Unix shell,
Atom,
Inkscape,
Quantum GIS,
ArcGIS,
Python (basic knowledge)

% Adobe Creative Suite,
% MacOS~X,
% Microsoft Office,
% Microsoft Windows
%
% \smallskip
% \emph{Basic knowledge}\newline%—would require some training/use to refresh my memory
% File Maker Pro Advanced,
% Gimp,
% Pixelmator

\bigskip
% \section{Certificates}
\mhead{Certificates}
\par\vspace{-\baselineskip}\begin{itemize*}
\item Wilderness and Remote First Aid \rdate{2016--2019}\\ Canadian Red Cross, St.\ John's, NL, Canada
\item WHMIS and Lab Safety \rdate{2017}\\ Memorial University of Newfoundland, St.\ John's, NL, Canada
\item Basic Outdoor First Aid \rdate{2014}\\ Marlin Training Ltd., London, UK
\item International English Language Testing System, grade 8.5 \rdate{2013}\\ British Council,Turin, Italy
\item International Computer Driving Licence \rdate{2007}\\ University of Turin,Turin, Italy
\end{itemize*}

\bigskip
% \section{Interests}
\mhead{Interests}%
Backpacking,
Hiking,
Photography,
Yoga
% ,
% T'ai Chi Quan,
% Shaolin Kung Fu

% % \newpage
% \bigskip
% % \section{References}
% \mhead{References}%
% \begin{minipage}[t]{.33\textwidth}
%   \raggedright
%   \textbf{Dr. Shawn J. Leroux}\\
%   Associate Professor,\\
%   Department of Biology\\
%   Memorial University of Newfoundland\\
%   St. John's, NL Canada\\
%
%   \noindent \href{mailto:sleroux@mun.ca}{sleroux@mun.ca}\\
%   tel: +1 (709) 864 3042\\
% \end{minipage}%
% % \begin{minipage}[t]{.33\textwidth}
% %   \raggedright
% %   \textbf{Dr. Yolanda F. Wiersma}\\
% %   Professor,\\
% %   Department of Biology\\
% %   Memorial University of Newfoundland\\
% %   St. John's, NL Canada\\
% %
% %   \noindent \href{mailto:ywiersma@mun.ca}{ywiersma@mun.ca}\\
% %   tel: +1 (709) 864 7499
% % \end{minipage}%
% \begin{minipage}[t]{.33\textwidth}
%   \raggedright
%   \textbf{Dr. Chelsea Little}\\
%   Assistant Professor,\\
%   School of Environmental Science\\
%   Simon Fraser University\\
%   Burnacy, BC Canada\\
%
%   \noindent \href{mailto:chelsea_little@sfu.ca}{chelsea\_little@sfu.ca}\\
%   tel: +1 (236) 978 0266
% \end{minipage}%
% \begin{minipage}[t]{.33\textwidth}
%   \raggedright
%   \textbf{Dr. Samraat Pawar}\\
%   Reader,\\
%   Department of Life Sciences\\
%   Imperial College London\\
%   London, UK
%
%   \noindent \href{mailto:s.pawar@imperial.ac.uk}{s.pawar@imperial.ac.uk}\\
%   tel: +44 (0) 2075 942 213
% \end{minipage}
\end{document}
